Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-29 ms.tex
added more explanation of the high res spectrum analysis and added the summary table from Van Lieshout et al. 2016.

\section{Subaru Analysis}

The host star \shStar\ has been characterized by both photometry and spectroscopy.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.

We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.

After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the Mg Triplet (Figure \ref{fig:mgTriplet}).
The Mg triplet is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
Also, we interpolated over any pixels above a normalized flux of 2.0 in Figure \ref{fig:mgTriplet} (top).
Then, we convolve with a Gaussian kernel with a standard deviation of 6 pixels.

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
There are many bad pixels.}\label{fig:naDline}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
First, the points above 2.0 are flagged as bad pixels and interpolated over.
Second, a convolution kernel is applied and the spectrum is compared to HIGHRES models.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

>>>>

\section{Stellar Characterization}

\subsection{Previous Observations}
The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.

\begin{deluxetable*}{lrrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}\label{tab:stellObsParams}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}
\end{deluxetable*}

\subsection{Observation}
\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
There are many bad pixels.}\label{fig:naDlines}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the

\subsection{Comparison to Templates}

The Mg Triplet (Figure \ref{fig:mgTriplet}) is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
Also, we interpolated over any pixels above a normalized flux of 2.0 in Figure \ref{fig:mgTriplet} (top).
Then, we convolve with a Gaussian kernel with a standard deviation of 6 pixels.

The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a much closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES.
The only mismatch between the 4500 K and log(g)=4.5 model and the HDS spectrum for \shStar\ is the overall line strengths.
